Analytic Doppler Imaging

### 2019-07-30 tex/gitlinks.tex
writing

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-07-30 tex/ms.tex
writing

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=1.0\linewidth]{figures/linalg.pdf}
    \oscaption{linalg}{%
        The linear Doppler imaging problem, $\bvec{f} = \bvec{D} \bvec{a}$.
        The vector on the left hand side, $\bvec{f}$, is the model for the
        observed flux, a sequence of $M$ spectra taken at different times,
        each measured at $K$ wavelength bins. The matrix on the right hand 
        side, $\bvec{D}$, is
        the Doppler design matrix, constructed from $M \times N$ Toeplitz
        matrices, each of shape $K \times (K + W)$, where $W$ is the width
        of the convolution kernel and $N$ is the number of spherical harmonic
        coefficients in the expansion of the stellar surface.
        The $N$ columns of $\mathcal{D}$ correspond
        to the Toeplitz matrices for each of the $N$ spherical harmonics;
        the $M$ rows correspond to the Toeplitz matrices rotated to each
        of the $M$ stellar phases observed. Finally, the vector at the 
        right is the weight vector $\bvec{a}$, a sequence of $N$ spectral 
        components, each of length $K + W$. In this example, each segment of
        $\bvec{a}$ is equal to a simple Gaussian line profile weighted by
        the spherical harmonic coefficients of a large equatorial starspot;
        this corresponds to a star whose spectrum is the same everywhere, but
        whose overall brightness varies spatially.
        \label{fig:linalg}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=1.0\linewidth]{figures/linalg_u.pdf}
    \oscaption{linalg_u}{%
        Similar to Figure~\ref{fig:linalg}, but isolating the linear dependence
        of the model on the spherical harmonic coefficients $\bvec{u}$.
        \label{fig:linalg_u}
    }
    \end{centering}
\end{figure}

>>>>

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=1.0\linewidth]{figures/linalg.pdf}
    \oscaption{linalg}{%
        The linear Doppler imaging problem, $\bvec{f} = \bvec{D} \bvec{a}$
        (Equation~\ref{eq:fDa}).
        The vector on the left hand side, $\bvec{f}$, is the model for the
        observed flux, a sequence of $M$ spectra taken at different times,
        each measured at $K$ wavelength bins (plotted to the left of $\bvec{f}$). 
        The matrix on the right hand 
        side, $\bvec{D}$, is
        the Doppler design matrix, constructed from $M \times N$ Toeplitz
        matrices, each of shape $K \times (K + W)$, where $W$ is the width
        of the convolution kernels (plotted at the top) and $N$ is the 
        number of spherical harmonic
        coefficients in the expansion of the stellar surface.
        The $N$ columns of $\mathcal{D}$ correspond
        to the Toeplitz matrices for each of the $N$ spherical harmonics;
        the $M$ rows correspond to the Toeplitz matrices rotated to each
        of the $M$ stellar phases observed (indicated graphically 
        to the left of $\mathbf{D}$). Finally, the vector at the 
        right is the weight vector $\bvec{a}$, a sequence of $N$ spectral 
        components, each of length $K + W$ (plotted to the right). 
        In this example, each segment of
        $\bvec{a}$ is equal to a simple Gaussian line profile weighted by
        the spherical harmonic coefficients of a large equatorial starspot;
        this corresponds to a star whose spectrum is the same everywhere, but
        whose overall brightness varies spatially.
        \label{fig:linalg}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=1.0\linewidth]{figures/linalg_u.pdf}
    \oscaption{linalg_u}{%
        Similar to Figure~\ref{fig:linalg}, but isolating the linear dependence
        of the model on the spherical harmonic coefficients:
        $\bvec{f} = \bvec{D}\bvec{V}\bvec{u}$ (Equation~\ref{eq:fDVu}).
        The $\bvec{f}$ vector and the $\bvec{D}$ design matrix are the same
        as before, but the spectra have been factored out 
        of the weight vector and into the $(N \times NP)$ matrix
        $\bvec{V}$, a block diagonal matrix constructed from $P$
        distinct spectral components (plotted at the top).
        \label{fig:linalg_u}
    }
    \end{centering}
\end{figure}
